---
title: "Paper planning for paper 3"
format:
    html:
        code-fold: true
        code-summary: "Show the code"
        code-tools: true
        theme: minty
---

## Purpose

Planning for the third paper regressions.

## Abstract

What are the effects of technological change on local labour markets? In this paper we seek to answer this question, leveraging a plausibly exogenous technology shock - the connection of the Western Line of the electricity grid between two hydropower stations in Sweden - that provided rural, otherwise unremarkable, parishes a stable and high-quality electricity connection prior to their neighbours. We motivate the exogeneity of this shock by documenting the geographic rollout of the grid through the first half of the 20th century and comparing attributes of the electrified parishes with a control group of parishes, prior to electrification.

We measure two individual-level outcomes nine years after the shock - migration status and income - with Swedish census data from 1930. We use a cross-section of individuals to measure the effect of electrification on the propensity to migrate and on earnings in the new parish for six distinct groups: the combination of a binary indicator for being born in an electricity parish (receiving the treatment) or not, an indicator for living in an electricity parish in 1930 or not, and an indicator for living in your parish of birth or not. Controls include geographic fixed effects, age, gender, and a HISCLASS grouping proxying social class.

Initial findings point to higher levels of migration in electricity parishes than in non-electricity parishes, particularly for prime working-age adults. We find a higher level of income for all individuals who no longer live in their parish of birth, indicating a wage premium for migration. In addition, we find that among those born in electricity parishes, the individuals who left their parish of birth and moved beyond the borders of an electricity parish saw the highest levels of income, on average, of our six groups. This indicates that the shock of electrification lowered the barriers to migration (should we speculate about this?) for individuals receiving the treatment of electrification.


## Intro

So far we just want to show the simple things. What has happened for the people who were born in electricity parishes, and then migrate?

## Pre-trends

The first thing we need to do is satisfy the concerns about our control and treatment groups prior to the rollout of electricity.

```{r}
library(tidyverse)
setwd(here::here())

df <- read_rds("data/augmented/df_1930_augmented.rds")

df <- df %>% 
  filter(tce_group_250 %in% c("control", "treatment"),
         adult_1930 == "Adult")
```

```{r}
df <- df %>% 
  mutate(female = case_when(
    kon == "K" ~ 1,
    kon == "M" ~ 0,
    TRUE ~ NA_real_
  ))

df <- df %>% 
  mutate(hisco_5_fact = case_when(
    hisco_5 == "Missing" ~ NA_character_,
    TRUE ~ hisco_5
  ))

df <- df %>% 
  mutate(hisco_5_fact = fct_relevel(hisco_5_fact, "Self-employed farmers and fishermen"))

df_reg <- df %>% filter(adult_1930 == "Adult")
```



We have the six groups we are interested in.

If you are born in an electricity parish and still live in your parish of birth.

If you are born in an electricity parish and you 

If you are born in an electricity parish 



HISCO classifications for those who were born in electricity parishes and moved

```{r}
df_movers_out <- df %>%
  filter(
    electricity_parish_born == 1,
    electricity_parish_living_in == 0
  ) %>%
  count(hisco_5) %>%
  filter(hisco_5 != "Missing") %>%
  mutate(group = "Movers out of electricity parishes")

df_movers_in <- df %>%
  filter(
    electricity_parish_born == 0,
    electricity_parish_living_in == 1
  ) %>%
  count(hisco_5) %>%
  filter(hisco_5 != "Missing") %>%
  mutate(group = "Movers into of electricity parishes")

df_movers_out %>%
  bind_rows(df_movers_in) %>%
  ggplot(aes(x = group, y = n, fill = hisco_5)) +
  geom_col(position = "fill") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    x = NULL,
    y = "Share of inhabitants",
    fill = "Occupational group"
  )
```


```{r}
df_movers_out <- df %>%
  filter(
    electricity_parish_born == 1,
    electricity_parish_living_in == 0
  ) %>%
  mutate(group = "Movers out of electricity parishes")

df_movers_in <- df %>%
  filter(
    electricity_parish_born == 0,
    electricity_parish_living_in == 1
  ) %>%
  mutate(group = "Movers into electricity parishes")

df_stayers_in <- df %>%
  filter(
    electricity_parish_born == 1,
    electricity_parish_living_in == 1
  ) %>%
  mutate(group = "Stayers in electricity parishes")

df_stayers_out <- df %>%
  filter(
    electricity_parish_born == 0,
    electricity_parish_living_in == 0
  ) %>%
  mutate(group = "Stayers in other parishes")


df_plot <- df_movers_out %>% 
  bind_rows(df_movers_in) %>% 
  bind_rows(df_stayers_in) %>% 
  bind_rows(df_stayers_out) 

df_plot %>% 
  filter(hisco_5 != "Missing") %>%
  ggplot(aes(log(inkomst), fill = group)) +
  geom_boxplot(alpha = .5) +
  facet_wrap(~hisco_5, nrow = 5) +
  labs(
    x = "Log income",
    fill = "Group",
    title = "Distribution of income by group"
  )
```


### Regressions


reg inkomst i.hisco_5_fact

* So relative to Unskilled workers and farm workers we see a big income premium. Good

* Now let's check how much of a hit you take for living in your parish of birth

reg inkomst lives_in_parish_of_birth i.hisco_5_fact age female if adult_1930 == 1

* So magnitude of the penality for living in your parish of birth is 353.67 / 819.23, 
* or 43% of the gender wage gap.


* What about the returns to migration by distance?

reg inkomst dist_bp_to_cp_km i.hisco_5_fact age female if adult_1930 == 1
reg inkomst dist_pp_to_cp_km i.hisco_5_fact age female if adult_1930 == 1



```{r}
library(gtsummary)

reg_out <- lm(inkomst ~ lives_in_parish_of_birth + hisco_5_fact + age + female, data = df_reg)

reg_out %>% gtsummary::tbl_regression() %>% 
  add_significance_stars() %>% 
  add_n()
```

Now include distance from birth parish to current parish instead of living_in_parish_of_birth

```{r}
reg_out <- lm(inkomst ~ dist_bp_to_cp_km + hisco_5_fact + age + female, data = df_reg)

reg_out %>% gtsummary::tbl_regression() %>% 
  add_significance_stars() %>% 
  add_n()
```


```{r}
df_magnitude <- df_reg %>%
  summarise(
    mean_dist_bp_to_cp_km = mean(dist_bp_to_cp_km, na.rm = T),
    median_dist_bp_to_cp_km = median(dist_bp_to_cp_km, na.rm = T),
    median_income = median(inkomst, na.rm = T)
  )

estimate <- reg_out %>% 
  broom::tidy() %>% 
  filter(term == "dist_bp_to_cp_km") %>% 
  pull(estimate)

library(gt)

df_magnitude %>%
  pivot_longer(-median_income) %>%
  mutate(
    estimate = estimate,
    effect_kr = value * estimate,
    effect_as_pct_median_income = effect_kr / median_income
  ) %>%
  select(name, effect_kr, effect_as_pct_median_income) %>%
  gt::gt()

```

So using the mean distance from birth parish to 

## Places of migration for the different people born in different places

```{r}
df_reg %>%
  filter(!is.na(hisco_5_fact)) %>%
  ggplot(aes(dist_bp_to_cp_km, fill = factor(electricity_parish_born))) +
  geom_density(alpha = .5) +
  scale_x_log10() +
  labs(
    x = "Distance from birth parish to current parish (km)",
    fill = "Born in electricity parish"
  ) +
  scale_fill_brewer(palette = "Dark2") +
  facet_wrap(~hisco_5_fact, nrow = 5) +
  theme(legend.position = "right")

df_reg %>%
  filter(!is.na(hisco_5_fact)) %>%
  group_by(
    electricity_parish_born,
    hisco_5_fact
  ) %>%
  summarise(
    mean_dist_bp_to_cp_km = mean(dist_bp_to_cp_km, na.rm = T),
    median_dist_bp_to_cp_km = median(dist_bp_to_cp_km, na.rm = T)
  ) %>%
  ungroup() %>%
  pivot_wider(names_from = electricity_parish_born, values_from = c("mean_dist_bp_to_cp_km", "median_dist_bp_to_cp_km")) %>%
    gt::gt() %>%
    fmt_number(decimals = 2, columns = -hisco_5_fact) %>%
    cols_label(
      hisco_5_fact = "",
      mean_dist_bp_to_cp_km_0 = "Outside Electricity Parish",
      mean_dist_bp_to_cp_km_1 = "Inside Electricity Parish",
      median_dist_bp_to_cp_km_0 = "Outside Electricity Parish",
      median_dist_bp_to_cp_km_1 = "Inside Electricity Parish"
    ) %>%
    tab_spanner(
      label = "Mean distance",
      columns = c(
        mean_dist_bp_to_cp_km_0, mean_dist_bp_to_cp_km_1
      )
    ) %>%
    tab_spanner(
      label = "Median distance",
      columns = c(
        median_dist_bp_to_cp_km_0, median_dist_bp_to_cp_km_1
      )
    ) %>%
    tab_header(
      title = md("Distances of migration"),
      subtitle = md("By place of birth and occupational class")
    )
  
```

```{r}
reg_out <- lm(dist_bp_to_cp_km ~ electricity_parish_born + hisco_5_fact + age + female, data = df_reg)

reg_out_2 <- lm(dist_pp_to_cp_km ~ electricity_parish_born + hisco_5_fact + age + female, data = df_reg)

reg_out <- reg_out %>%
  gtsummary::tbl_regression() %>%
  add_significance_stars() %>%
  add_n()

reg_out_2 <- reg_out_2 %>% 
    gtsummary::tbl_regression() %>%
  add_significance_stars() %>%
  add_n()

tbl_merge(tbls = list(reg_out, reg_out_2))

```

Do people born in electricity parishes see a higher return to migration the same distance?

So we want to run a regression where income is dep var, and indepvar of interest is electricity_parish_born

```{r}
reg_out <- lm(inkomst ~ electricity_parish_born + dist_bp_to_cp_km + hisco_5_fact + age + female, data = df_reg)

reg_out %>%
  gtsummary::tbl_regression() %>%
  add_significance_stars() %>%
  add_n()
```

Map of their migrations by social class

```{r}
library(sf)
setwd(here::here())


st_map <- read_rds("data/st_map.rds") %>% 
  mutate(scbkod = as.numeric(ref_code_char)) %>% 
  st_transform(crs = 4326)
  
df_map <- st_map %>% 
  inner_join(df_reg %>%
  filter(
    electricity_parish_born == 1,
    lives_in_parish_of_birth == 0
  ) %>%
  count(scbkod))

library(leaflet)
  
bins <- c(0, 10, 20, 50, 100, 200, 500, 1000, Inf)
pal <- colorBin("viridis", domain = df_map$n, bins = bins)

labels <- sprintf(
  "<strong>%s</strong><br/>%.0f Number of people moving from electricity parishes",
  df_map$name, df_map$n
) %>% lapply(htmltools::HTML)


leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolygons(
    data = df_map,
    fillColor = ~ pal(n),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlightOptions = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    popup = labels,
  ) %>%
  addLegend("bottomright",
    pal = pal, values = df_map$n,
    title = "Number of people moving from electricity parishes"
  )

```



```{r}
# df %>%
#   filter(adult_1930 == "Adult") %>%
#   group_by(type_born, migrant) %>%
#   summarise(mean_income = round(mean(inkomst, na.rm = T))) %>%
#   ungroup() %>%
#   ggplot(aes(type_born, migrant)) +
#   geom_tile(aes(fill = mean_income)) +
#   geom_label(aes(label = mean_income)) +
#   labs(
#     title = "Mean income",
#     subtitle = "By parish of birth type",
#     x = "Parish type which individuals were born in",
#     y = "Left parish of birth?"
#   )
```

Maybe we need to think about the group that comes in 
