---
title: "02-analysis"
format: html
---

We want to do a basic cross tab map - Compare population change by parish to access to electricity. 

Need 1910 census ad 1930 census.

```{r}
df_census <- read_rds("data/population_by_parish_1880_1930")

parish_sample <- df_census %>%
  distinct(ref_code_char) %>%
  slice_sample(n = 30) %>% 
  pull()

df_census %>% 
  pivot_longer(-ref_code_char) %>% 
  mutate(name = parse_number(name)) %>% 
  filter(ref_code_char %in% parish_sample) %>% 
  ggplot(aes(name, value, colour = ref_code_char)) +
  geom_line() +
  scale_y_log10()
```

Map:

```{r}
library(histmaps)
data("geom_meta")
library(sf)
p_map <- get_boundaries("1910", "parish")
st_map <- p_map %>% left_join(geom_meta, by = c("geom_id"))
st_map <- st_map %>% 
  mutate(ref_code_char = str_remove(ref_code.x, "SE/"),
         ref_code_char = str_sub(ref_code_char, end = -4))
```

Census changes:

```{r}
df_census_changes <- df_census %>%
  mutate(
    mon_inc = case_when(
      x1880 < x1890 & x1890 < x1900 & x1900 < x1910 ~ 1,
      x1910 < x1900 & x1900 < x1890 & x1890 < x1880 ~ -1,
      TRUE ~ 0
    ),
    pct_change_1880_1910 = 100 * (x1910 - x1880) / x1880
  )

df_census_changes_map <- df_census_changes %>% 
  select(ref_code_char, mon_inc, pct_change_1880_1910) %>% 
  inner_join(st_map)
```

What do we find first?

```{r}
df_census_changes_map %>% 
  # filter(county == 15) %>%
  ggplot(aes(fill = mon_inc, geometry = geometry)) +
  geom_sf(colour = "black") +
  scale_fill_gradient2() +
  labs(title = "Increasing population and decreasing population",
       subtitle = "In Sweden from 1880 to 1910")

df_census_changes_map %>% 
  filter(county == 5) %>%
  st_bbox(geometry)
  ggplot(aes(fill = pct_change_1880_1910, geometry = geometry)) +
  geom_sf(colour = "black") +
  scale_fill_gradient2(labels = scales::percent_format(scale = 1))

```


```{r}
library(ggmap)

b_box_nigeria <- c(left = 2, bottom = 3, right = 15, top = 14)
nigeria_map <- get_map(b_box_nigeria, zoom = 6)

ggmap(nigeria_map) 

```



Need to work out how to do the intersection thing between the grid and then highlight the counties that do have the intersection at a particular time to track changes. 


just show change in population by county in the two groups over the different time periods:1910 to 1930. 

We need the knowledge of the assignment mechanism: does being on the central line increase available power and when? 

obviously we need to have the invention of three phase AC to transmit over long distances. 

If the power generated is DC - it is to be used locally. If AC - then far transmission. Is there a correlation between the areas with lot's of DC power and the areas with a lot of grid cables??


