---
title: "Untitled"
format: html
---

## Purpose

Cleaning up the occupational colmn in the census data.

For CIV -

G is gift - marrid
O is ogift - unmarried
E is widow or widower
X is divorced (on the basis of investigating different people)
U is in the unknown book - there are just 67 of them. 

hos 
vid 
f.d. former

What should we put in each column

Widow - former, 

If missing - check the column ovf_obef_ar

### Notes


fd - före detta - ex - job title. 

Åboänka Undantagsman (farmer and then does something else = Åbo can stay on the farm - they have the right)

Accidenstryckare who prints advertising and such - not newspapers, not books. Commercial papers. Forms. 

Ackumulatorarbetare - energy storage device worker

förman is a supervisor. Arbetare is just a worker. biträde is an assistant. 

Ackuschörska - förlossnings läkare - somewhere between midwife and a doctor

Adjunkt - teacher but higher. 

ägare is owner.  Direktör is md.

Affärsman  - businessman.

Grosshandelsrörelse - merchant.

Ägare Änka Undantag - Undantag - you have the right to stay on part of your property - you make a contract. As previous owner you can do it with your children - or someone else. 

Arrendator - tennant farmer usually, could be tennant of something else.

innehaverska - 

Affärsinnehaverska - owns a shop. takes care of a shop. innehaverska just means she runs the establisment.

Innehavare - male form of a 

änka is a widow
änkling (widower)

frånskild is divorced

i faderns affär - in fathers shop

Konsum - coop

mjölkcentral - where you make cheese and cream and butter.

Speceri - groceries

Utan anställning - without employment

 f.n. - just now. för närvarande
 
havarinna vs havarska. innehavarinna is the never form of innehaverska

House owner is the default title if you didn't own anything else.

Gjutare - factory worker who casts.

Rättare  - one who supervises a farm. a bigger farm.

Handlande - remove ägare 

A number contain  f.d. showing they used to be somehing.

Hönsskötsel - takes care of the chickens.

Järnarbetare - steelworker.

Järnvägsarbetare - railway worker.

Kapitalist - someone who lives on their own money. they don't have to work.

Agronom - farmer but with higher education.

Some are a mix between profession or marital status.

Separate these out.

Think about the transitions

Fattighjon Hemmansägaredotter f.d. - should exclude the second part.


### Divorced

frsk as frånskild 

### Dairy

Mejerinna - Mejerist is a man who works in a dairy. This is the female. She is above the jungfru and the elev of the same.

### A stall by the road

Bod like bodgumma. a tent at which you sell something. 

Restautantrice - a french word for a lady who runs a restaurant. 

### Pappersbruk

There are lots of specific titles within the paper mill. Maybe have a look at them separetly. 


### What is a good way to do this? Look for the most common parts of the occupational descriptions.

```{r}
library(tidyverse)
library(tidytext)

parts <- df_reg %>% 
  select(yrke) %>% 
  distinct()

parts

```



What does the classification of occupations look like from the original census

```{r}
df_reg

df_reg %>% 
  count(yrkkod, sort = T) %>% view()

df_reg %>% 
  count(yrke, yrkkod)

df_reg %>% 
  filter(yrkkod == "1.2") %>% view()

df_reg %>% 
  filter(yrkkod == "") %>% 
  count(yrke, sort = T)

df_reg %>% 
  filter(yrke == "Hembiträde") %>% 
  count(yrkkod, sort = T)

df_reg %>%
  filter(yrkkod == "3.2") %>% 
  select(yrke)

df_reg %>% 
  filter(str_detect(yrke, "handlare")) %>% 
  count(yrkkod, sort = T)

df_reg %>% 
  filter(yrkkod == "2.A.4") %>% 
  select(yrke) %>% distinct()
```

Qestion: how does 2.D.12 differ from 2.D.27

```{r}

df_reg %>%
  filter(yrkkod %in% c("2.D.12", "2.D.27")) %>%
  select(yrke, yrkkod) %>%
  count(yrkkod, yrke, sort = T)

```



```{r}
df_reg %>%
  filter(str_detect(yrkkod, "1.14")) %>%
  select(yrke) %>%
  distinct()

df_reg %>%
  filter(str_detect(yrkkod, "4.25")) %>%
  select(yrke)

df_reg %>% 
  filter(str_detect(yrke, "Badmästare")) %>% 
  count(yrkkod)
```


Let's check for how many specific occupational strings there are different occupational codes

```{r}
df_reg %>% 
  group_by(yrke) %>% 
  count(yrkkod, sort = T)

```

