---
title: "1930 census 's.e. investigation'"
format: pdf
execute: 
  echo: false
  message: false
  warning: false
---

## Purpose

Investigate the prevalence of s.e. in the 1930 census occupational titles

## Context

According to Anders and Björn "apparently, it should be short for “sin egen” that means that you are not employed, but instead run your own business."

## How common is it?

```{r}
library(tidyverse)
library(gt)
theme_set(theme_light())

# df <- read_rds(here::here("data/augmented/df_1930_augmented.rds"))
df <- read_rds(here::here("data/temp/se_investigation.rds"))

```

How many different ways is it written?

```{r}
tibble(type = c("se", "se.", "s.e."),
       n = c(57, 233,  7293),
       pattern = c(" se$| se ", " se\\.", "s\\.e\\.")) %>% 
  select(!pattern) %>% 
  gt() %>% 
  fmt_number(n, decimals = 0, sep_mark = " ") %>% 
  tab_header(title = md("**How common is 's.e.' in occupational titles**"),
             subtitle = "In the swedish 1930 census") %>% 
  cols_label(type = "Written",
             n = "Number of records")
```

What are the most common titles for which it occurs?

```{r}
df %>%
  select(yrke.x, yrke.y, scbkod) %>%
  count(yrke.y, sort = T) %>%
  filter(!is.na(yrke.y)) %>%
  mutate(yrke.y = fct_reorder(yrke.y, n)) %>%
  slice_head(n = 20) %>%
  ggplot(aes(n, yrke.y, fill = n)) +
  geom_col(show.legend = F) +
  scale_fill_viridis_c() +
  labs(x = "Number of observations", 
       y = "Title")

```

### Where is it common?

```{r}
library(sf)
st_map <- readRDS(here::here("Electricity-control-groups/st_map.rds"))

se_places <- df %>%
  filter(str_detect(yrke.x, " se\\.| s\\.e\\.| se$| se ")) %>%
  select(yrke.x, yrke.y, scbkod) %>% 
  count(scbkod)

df_map_counts <- st_map %>% 
  mutate(scbkod = str_remove(ref_code.x, "SE/"),
         scbkod = str_remove(scbkod, "\\d\\d\\d$"),
         scbkod = as.numeric(scbkod)) %>% 
  inner_join(se_places, by = c("scbkod"))
```


```{r}
ggplot() +
  geom_sf(data = st_map, fill = "grey80", colour = "#FFFFFF") +
  geom_sf(aes(fill = n), data = df_map_counts) +
  scale_fill_viridis_c() +
  labs(fill = "Number of records with s.e.")
```

It doesn't seem like it any specific geographical pattern that differs from population.

```{r}
df_map_counts %>%
  as_tibble() %>%
  select(name, n) %>%
  arrange(desc(n)) %>%
  slice_head(n = 20) %>%
  mutate(name = fct_reorder(name, n)) %>%
  ggplot(aes(n, name, fill = n)) +
  geom_col(show.legend = F) +
  labs(
    n = "Number of records with s.e.",
    y = "Parish"
  )
```


