---
title: "23-Recreating-MPTTP"
format: html
---

## Purpose

Recreate the results of More Power to the People.

### Data

They create a panel - 3 time periods. Compare parishes over time because their variation is at the parish level.

3 sources of data. 

1. Geocoded strike data. Measured at the parish level.

2. Occupational structure of each parish from IPUMS international.

3. Access to the grid from digitized maps.

### Panel dataset on 2,470 parishs at unchanging level.

Main outcome variable: strikes. 

Mechanisms from electricity to strikes - strutural change

### Definition of Western Line

"Due to the exogenous nature of the location of power plants and the explicit intention to connect Olidan to älvkarleby via a state-sponsored mainline system, the Western Lin, we consider parishes connected to the first mainline system, the Western Line, and within a 60-km buffer along a straing line between the two power plants as our main treatment variable. 

The sample from the Western Line consists of 192 parishes and is depicted with thick lines in figure 1.

### Tabstat

```{r}
library(tidyverse)
library(haven)

parishes_1900 <- read_dta(here::here("replication", "data", "data Table 2.dta"))

parishes_1900 %>% view()
```

Stata:
* create table with the mean and standard deviation of each variable by later access to the grid
tabstat labforce shc1 shc2 shc3 shc4 shc5 shc6 shc7 strikes strikesoff strikesdef, by(ever_iline) format(%5.0g) stat(mean sd)

* test for difference-in-means 
foreach var of varlist labforce shc1 shc2 shc3 shc4 shc5 shc6 shc7 strikes strikesoff strikesdef {
ttest `var', by(ever_iline) 
}

```{r}
# Table 2
library(broom)
library(gt)

parishes_1900_means <- parishes_1900 %>%
  group_by(ever_iline) %>%
  summarise(across(labforce:shc7, .fns = list(
    mean = ~ mean(.x, na.rm = T),
    sd = ~ sd(.x, na.rm = T)
  ))) %>%
  pivot_longer(-ever_iline) %>%
  separate(name, into = c("variable", "stat"), sep = "_") %>%
  pivot_wider(names_from = ever_iline, values_from = value)


parishes_1900_ttest <- parishes_1900 %>%
  pivot_longer(labforce:shc7, names_to = "variable", values_to = "value") %>%
  group_by(ever_iline, variable) %>%
  nest() %>%
  spread(key = ever_iline, value = data) %>%
  mutate(
    t_test = map2(`0`, `1`, ~ {
      t.test(.x$value, .y$value) %>% tidy()
    }),
    `0` = map(`0`, nrow),
    `1` = map(`1`, nrow)
  ) %>%
  unnest(cols = everything()) %>%
  ungroup()

parishes_1900_ttest <- parishes_1900_ttest %>%
  select(variable, estimate, p.value) %>%
  mutate(estimate = -estimate) %>%
  pivot_longer(-variable)

parishes_1900_means %>%
  select(-stat) %>%
  bind_cols(parishes_1900_ttest %>% select(-name, -variable)) %>%
  gt()


```


## Now checking for comparisons with treatment group

```{r}
groups_1930 <- df %>% select(arkbild, scbkod, contains("tce_group")) %>% distinct()


parishes_1900 <- parishes_1900 %>%
  mutate(
    parish_code_short = as.character(parish_code),
    parish_code_short = str_remove(parish_code_short, "[0-9][0-9][0-9]$"),
    parish_code_short = as.numeric(parish_code_short)
  )

groups_1930 <- groups_1930 %>% 
  inner_join(parishes_1900, by = c("scbkod" = "parish_code_short"))
```


```{r}
library(gtsummary)

groups_1930 %>%
  select(ever_iline, labforce:shc7) %>%
  drop_na() %>%
  tbl_summary(by = ever_iline, statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} ({p}%)")) %>%
  add_difference() %>%
  add_significance_stars()
```

