---
title: "20th April Talk"
format: html
---

## Purpose

- Broad and interesting talk
- What does economic history tell us about new technology.

My prompt:

I have a dataset of people in the Swedish Census of 1930. I am interested in electrification - I have a sample of parishes that got access to electricity prior to their neighbouring parishes and who as a result could see their inhabitants sort into electricity related jobs at higher rates than their neighbours. I have now got a list of jobs, those that are directly electricity related, indirectly related to electricity, and not related. I want to ask a question like "how did the incomes of the three groups differ between electricity and non-electricity parishes?" and "Did the workers in the three groups migrate in to the electricity parishes from different areas?" which I think I can answer with my dataset.


## Analysis plan:

### 1. Data preparation:

a. Clean and preprocess the dataset, if necessary.

b. Ensure that the dataset includes the relevant variables for your analysis, such as job type, income, parish, electrification status, and migration information.

c. Categorize jobs into the three groups: directly electricity-related, indirectly related, and not related.

d. Create a binary variable for electrification status (1 if a parish has access to electricity, 0 otherwise). 


```{r}
# read in data
# cleaning is done elsewhere
library(tidyverse)
theme_set(theme_light())
df_reg <- read_rds(here::here("data", "clean_data", "df_ref.rds"))

library(showtext)
library(ggtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("IBM Plex Mono", "ibm")
font_add_google("Roboto", "roboto")

showtext_opts(dpi = 300)
showtext_auto(enable = TRUE)

```


```{r}
# relevel occupational groups - 
df_reg <- df_reg %>%
  mutate(
    hisclass_group_abb = fct_relevel(hisclass_group_abb, "Farmers and fishermen"),
    age_2 = age^2) %>%
    mutate(across(.cols = c(income_incl_zero, income_imputed_mean, income_imputed_median), log, .names = "log_{.col}"))

# select just the treatment and control individuals within the 250 km band
df_reg_250 <- df_reg %>%
  filter(
    tce_group_250 %in% c("control", "treatment"),
    adult_1930 == "Adult"
  )
```

```{r}
# c. Categorize jobs into the three groups: directly electricity-related, indirectly related, and not related.

df_reg_250 <- df_reg_250 %>%
  mutate(electricity_direct = case_when(
    str_detect(yrke.y, regex("elektr", ignore_case = TRUE)) ~ 1,
    yrke.y == "Elmontör" ~ 1,
    str_detect(yrke.y, "Linjearbetare") ~ 1,
    str_detect(yrke.y, "Kraftverksarbetare") ~ 1,
    TRUE ~ 0
  ))
```


```{r}
df_reg_250 <- df_reg_250 %>%
  mutate(electricity_indirect = case_when(
    yrke.x %in% c(
      "Maskinist",
      "Pappersbruksarbetare",
      "Verkstadsarbetare",
      "Metallarbetare",
      "Textilarbeterska",
      "Sömmerska s. e.",
      "Träarbetare",
      "Järnverksarbetare",
      "Montör",
      "Valsverksarbetare",
      "Sömmerska s.e.",
      "Bryggeriarbetare",
      "Gjuteriarbetare",
      "Rörverksarbetare",
      "Smidesarbetare",
      "Pappersfabriksarbetare",
      "Maskinarbetare",
      "Plåtslageriarbetare",
      "Filare",
      "Skofabriksarbetare",
      "Järnbruksarbetare",
      "Slakteriarbetare",
      "Svarvare",
      "Glasslipare",
      "Tegelarbetare",
      "Snickerifabriksarbetare",
      "Färgeriarbetare",
      "Järnsvarvare",
      "Mejeribiträde",
      "Sågverksarbetare",
      "Tegelfabriksarbetare",
      "Mejerist",
      "Fabriksarbeterska",
      "Smedsarbetare",
      "Träsliperiarbetare",
      "Filare",
      "Sågare",
      "Mekaniker",
      "Tändsticksfabriksarbetare",
      "Telefonarbetare",
      "Skoarbetare",
      "Metallarbetare",
      "Snickeriarbetare",
      "Trämassearbetare",
      "Maskinsnickare",
      "Pappersbruksarbetare",
      "Textilarbetare Vävare",
      "Smedmästare",
      "Textilarbetare väv.",
      "Spinnerska",
      "Gjuteriarbetare",
      "Möbelsnickeriarbetare",
      "Tillskärare",
      "Pressare",
      "Mekanisk verkstadsarbetare",
      "Tandtekniker",
      "Varvsarbetare",
      "Martinarbetare",
      "Textilfabriksarbetare",
      "Järnvägsverkstadsarbetare",
      "Valsverksarbetare vid järnbruk",
      "Fabriksarbetare",
      "Smed s. e.",
      "Maskinist",
      "Sulfitfabriksarbetare",
      "Verkstadsarbetare",
      "Montör",
      "Tändsticksfabriksarbeterska",
      "Plåtverksarbetare",
      "Kopparslagare",
      "Lådfabriksarbetare",
      "Textilfabriksarbetare",
      "Gjutare",
      "Pappersarbetare",
      "Smedslärling",
      "Bilmontör",
      "Ingenjör",
      "Fabrikör",
      "Spolerska",
      "Textilfabriksarbeterska",
      "Hyttarbetare",
      "Smältverksarbetare",
      "Möbelfabriksarbetare",
      "Svarvare",
      "Tobaksarbetare",
      "Tråddragare",
      "Smed",
      "Konfektionssömmerska",
      "Pressare",
      "Bageriarbetare",
      "Slöjdare",
      "Kartongarbetare",
      "Verkmästare",
      "Sulfitfabriksarbetare",
      "Modellsnickare",
      "Plåtslagare",
      "Spinnare",
      "Järnsvarvare",
      "Ritare",
      "Tändsticksfabriksarbetare",
      "Skofabriksarbetare",
      "Motorskötare",
      "Appretörarbetare",
      "Chokladarbetare",
      "Maskinarbetare",
      "Trikåfabriksarbetare",
      "Cellulosafabriksarbetare",
      "Slaktare s.e.",
      "Bleckslagare",
      "Sockerbruksarbetare",
      "Telefonreparatör",
      "Garvare",
      "Linnesömmerska",
      "Trämassefabriksarbetare",
      "Martins-arbetare vid järnbruk",
      "Spikfabriksarbetare",
      "Spinneriarbetare",
      "Smidesarbetare",
      "Svetsare",
      "Korsettarbetare",
      "Yllefabriksarbetare",
      "Masugnsarbetare",
      "Smörjare",
      "Cellulosafabriksarbetare ",
      "Tryckeriarbetare",
      "Slipmassefabriksarbetare",
      "Reparatör",
      "Tegelbruksarbetare",
      "Bryggeriarbetare",
      "Smedarbetare",
      "Mekanikerarbetare",
      "Glasverksarbetare",
      "Textilarbetare Väverska",
      "Pälssömmerska",
      "Kalkbruksarbetare",
      "Bleckslageriarbetare",
      "Polerare",
      "Sågverksägare",
      "Faktor",
      "Stålverksarbetare",
      "Textilarbetare Rullerska",
      "Jutefabriksarbeterska",
      "Verktygsarbetare",
      "Rullerska",
      "Armaturarbetare",
      "Cementfabriksarbetare",
      "Hyvlare",
      "Litografiarbeterska",
      "Sågarbetare",
      "Fräsare",
      "Textilarbetare väveri",
      "Sågmästare",
      "Fabrikssömmerska",
      "Tegelarbetare",
      "Sortererska vid pappersbruk",
      "Tricotstickerska",
      "Laboratoriebiträde",
      "Textilarbetare Spinnare",
      "Fabriksarbetare papp.",
      "Stickerska s.e.",
      "Hemsömmerska",
      "Maskinpassare vid pappersbruk",
      "Varvsarbetare",
      "Rördrageriarbetare vid järnbruk",
      "Plåtslageriarbetare",
      "Emaljarbetare",
      "Tvinnerska",
      "Sågverksförman",
      "Sömmerska s. e.",
      "Trikåarbetare",
      "Kaolinbruksarbetare",
      "Fanerfabriksarbetare",
      "Lådfabriksarbetare",
      "Textilarbetare Sömmerska",
      "Textilarbetare Spolerska",
      "Maskinstickerska",
      "Fabriksarbetare cellulosafabrik",
      "Trämassefabriksarbetare",
      "Ritare",
      "Typograflärling",
      "Kappsömmerska",
      "Sömmerska textil",
      "Jutefabriksarbetare",
      "Fabriksarbeterska",
      "Fabriksarbetare sulfatfabrik",
      "Fabriksarbeterska Väverska",
      "Möbelfabrikör",
      "Klensmed",
      "Maskinförare vid pappersbruk",
      "Plåtslageriarbetare M. V.",
      "Tillskärerska",
      "Maskinskötare",
      "Smidesmästare",
      "Margarinfabriksarbetare",
      "Gummifabriksarbetare",
      "Maskinförare",
      "Skomakeriarbetare",
      "Avsynare",
      "Läderarbetare",
      "Karamellfabriksarbetare",
      "Plåtarbetare",
      "Metallduksvävare",
      "Tråddrageriarbetare",
      "Sömmerska Hemmadotter",
      "Snickeriförman",
      "Kappfabrikssömmerska",
      "Borrare",
      "Tryckare",
      "Borrare",
      "Sömmerska s.e.",
      "Snickerifabrikör",
      "Svarvare Arbetare",
      "Valsare",
      "Mejerinna",
      "Smärglare",
      "Smältare",
      "Brädgårdsförman",
      "Kakelfabriksarbetare",
      "Varperska",
      "Konservfabriksarbetare",
      "Mekaniker",
      "Svetsare",
      "Gjutmästare",
      "Järnsvarvare M. V.",
      "Kopparslageriarbetare",
      "Maskinsnickeriarbetare",
      "Karamellarbetare",
      "Kranmaskinist ",
      "Maskinmästare",
      "Smedsdräng",
      "Textilarbetare",
      "Snickare vid möbelfabrik",
      "Torvströfabriksarbetare",
      "Smedmästare ag.",
      "Bilmontör",
      "Guldlistarbetare",
      "Västsömmerska",
      "Sågverksarbetare f.",
      "Underofficer Maskinist",
      "Tråddrageriarbetare vid järnbruk",
      "Fabrikssnickare",
      "Tekniskt biträde",
      "Fabriksarbetare vid Kallvalsverk",
      "Spårvagnskonduktör",
      "Smedsgesäll",
      "Väveriarbetare",
      "Borstbinderiarbetare",
      "Textilförman",
      "Verkstadsförman",
      "Bobinfabriksarbetare",
      "Cykelarbetare",
      "Sågställare",
      "Plyserska",
      "Linderska",
      "Plåtslagare vid mekanisk verkstad",
      "Väverska textilfabrik",
      "Sorterare",
      "Galvaniseringsarbetare",
      "Industriarbetare",
      "Tricotsömmerska",
      "Beredningsarbetare",
      "Kopparslagare",
      "Väverska",
      "Maskinsättare",
      "Väverska textil",
      "Syfabrikssömmerska",
      "Lokomotivförare",
      "Radiotelegrafist",
      "Tunnfabriksarbetare",
      "Linjearbetare",
      "Plåtslagare s. e.",
      "Sågägare",
      "Sågverksmaskinist",
      "Maskinmjölkare",
      "Kranförare",
      "Maskinformare",
      "Telefonföreståndare",
      "Plåtslagare s.e.",
      "Barkhusarbetare Pappersbruk",
      "Eldare vid pappersbruk",
      "Textilarbetare varp.",
      "Kullagerarbetare",
      "Gravör",
      "Kärnmakare",
      "Väverska s. e.",
      "Sliparbetare",
      "Glödgare",
      "Lokförare järnväg",
      "Radiomontör",
      "Linslagare",
      "Diversearbetare Pappersbruk",
      "Sockerfabriksarbetare",
      "Porslinsfabriksarbetare",
      "Sömmerska Skräddare",
      "Tobaksarbeterska",
      "Stålsynare vid järnbruk",
      "Chokladarbeterska",
      "Facitarbetare",
      "Stabbläggare",
      "Mejerska",
      "Stenarbetareänka",
      "Tricotarbetare",
      "Silverpolererska",
      "Mejeribiträde",
      "Träindustriarbetare",
      "Maskinarbetare vid snickerifabrik",
      "Tapetfabriksarbetare",
      "Stenkrossarbetare",
      "Kartongfabriksarbetare",
      "Brukstjänsteman",
      "Glaspackare",
      "Möbelfabrikssnickare",
      "Fabriksarbetare Ägare",
      "Järnarbetare mekanisk verkstad",
      "Verkstadsarbetare Filare",
      "Gummireparatör",
      "Textilarbeterska",
      "Diamantborrare",
      "Rorgängare",
      "Textilarbetare kamgarnspinneri",
      "Bänkarbetare",
      "Cellulosafabriksarbetare Diversearbetare",
      "Sockerbruksarbetare",
      "Gjutare M. V.",
      "Övermaskinist",
      "Spiksmed",
      "Fräsare",
      "Gummiarbetare",
      "Margarinarbetare",
      "Klädesfabriksarbetare",
      "Bleckslageriarbetare",
      "Textilarbetare Appretör",
      "Ackumulatorsfabriksarbetare",
      "Lastare",
      "Bergsingenjör",
      "Porslinsarbetare",
      "Spinnare textil",
      "Urmakare",
      "Rensare",
      "Konfektionsarbetare",
      "Smärglare",
      "Repslageriarbetare",
      "Sömmerska Konfektion",
      "Vävare yllefabrik",
      "Sömnadsarbetare",
      "Borstarbetare",
      "Lagersömmerska",
      "Verkstadsarbetare vid järnbruk",
      "Verkstadsarbetare vid järnbruk",
      "Träullfabriksarbetare",
      "Järnarbetare Pappersbruk",
      "Synerska",
      "Konfektionspressare",
      "Stålvägare vid järnbruk",
      "Sömnadsarbeterska",
      "Glasarbetare",
      "aaaa",
      "Spolerska textil",
      "Mekanikerarbetare",
      "Glasskärare",
      "Rullerska textil",
      "Mek. arbetare",
      "Sågare",
      "Maskinreparatör",
      "Gödningsfabriksarbetare",
      "Glasslipare",
      "Reparatör vid pappersbruk",
      "Vävare textilfabrik",
      "Plåtslageriarbetare v. mek. verkst.",
      "Silverpolererska",
      "Tvålfabriksarbetare",
      "Gårdfarihandlare",
      "Sömmerska fabrik",
      "Biografmaskinist",
      "Textilarbetare Spolare",
      "Sömnadsarbetare",
      "Martinsarbetare",
      "Manglerska",
      "Litograf",
      "Sågbladsarbetare vid järnbruk",
      "Textilarbetare Tvisterska",
      "Byxsömmerska",
      "Väverska yllefabrik",
      "Hattfabriksarbetare",
      "Dussinsömmerska",
      "Kragsömmerska",
      "Cellulosafabriksarbetare Reparatör",
      "Lagerbiträde textil",
      "Litografarbetare",
      "Filhuggare",
      "Rullare vid pappersbruk",
      "Skofabriksarbeterska",
      "Fabriksarbetare cellulosa",
      "Putsare Arbetare",
      "Kantsågare",
      "Galvanisör",
      "Ingeniör",
      "Elektriker Montör",
      "Bindgarnsarbetare",
      "Bruksarbetare Gjutare",
      "Lackerare",
      "Sömmerska duss.",
      "Sättare",
      "Sömmerskearbetare",
      "Mejerimaskinist",
      "Varvsplåtslagare",
      "Filhuggare",
      "Stålsynare",
      "Hyttarbetare Järnverk",
      "Makaroniarbetare",
      "Magasinarbetare",
      "Pappersbrukfabriksarbetare",
      "Väskfabriksarbetare",
      "Textilarbetare Varperska",
      "Marmeladarbeterska",
      "Klädsömmerska",
      "Textilsömmerska",
      "Fabriksarbetare vid järnbruk",
      "Torkare vid pappersbruk",
      "Spinnerska textilfabrik",
      "Sömmerska se.",
      "Fabriksförman",
      "Utearbetare vid sulfitfabrik",
      "Textilfabriksarbeterska",
      "Tillskärare",
      "Mjölkning",
      "Tyglagerska yllefabrik",
      "Stickerska textil",
      "Typograf Sättare",
      "Textilarbetare Färgare",
      "Sintringsarbetare",
      "Påsfabriksarbetare",
      "Järnarbetare Kockum",
      "Sömmerska trikåfabrik",
      "Färgeriarbetare textil",
      "Konfektionsfabrikssömmerska",
      "Fabriksarbetare pappersbruk",
      "Sågförman",
      "Grovarbetare vid järnbruk",
      "Förtennare",
      "Vaddfabriksarbetare",
      "Tricotstickare",
      "Pressare konfektion",
      "Cellulosafabriksarbetare",
      "Presserska",
      "Instrumentmakare",
      "Reparatör Pappersbruk",
      "Segelsömmare",
      "Sömmerska vid fabrik",
      "Fabriksarbetare Eldare",
      "Torvfabriksarbetare",
      "Bindgarnsarbeterska",
      "Styckmästare",
      "Civilingenjör",
      "Vävare textil",
      "Stenslipare",
      "Tillskärare konfektion",
      "Maskinmontör",
      "Textilarbetare Solverska",
      "Maskinist vid sågverk",
      "Motorförare",
      "Hjälpmontör",
      "Väverska Holm. br.",
      "Revolversvarvare",
      "Varvsförman",
      "Sömmerska vid fabrik",
      "Järnarbetare vid pappersbruk",
      "Fabriksarbetare Eldare",
      "Gjuteriarbetare M. V.",
      "Torvfabriksarbetare",
      "Spisbrödsfabriksarbetare",
      "Bindgarnsarbeterska",
      "Sågverksarbetare Diversearbetare",
      "Civilingenjör",
      "Cementgjuteriarbetare",
      "Vävare textil",
      "Tillskärare konfektion",
      "Verkstadsägare",
      "Maskinmontör",
      "Textilarbetare Solverska",
      "Verksarbetare",
      "Maskinist vid sågverk",
      "Bryggeriägare",
      "Martins-arbetare",
      "Vällare",
      "Vattenfabriksarbetare",
      "Glasarbetare Slipare",
      "Järnarbetare Filare",
      "Gjuterihantlangare",
      "Manufakturarbetare",
      "Mejslare",
      "Trävaruarbetare",
      "Typograf Tryckare",
      "Telefonstationsföreståndarinna",
      "Sömmerska herrkonfektion",
      "Maskinförman",
      "Mejerist Föreståndare",
      "Resårfabriksarbetare",
      "Dessinatör",
      "Kärnmakare Arbetare",
      "Smed vid stenhuggeri",
      "Grovarbetare Pappersbruk",
      "Brädgårdsarbetare Stabbläggare",
      "Maskinslipare",
      "Sågverksarbetare Lägenhetsägare",
      "Snickeriarbetare Möbel",
      "Fabriksarbetare Pappersbruk",
      "Förman Pappersbruk",
      "Tändsticksfabriksförman",
      "Verkstadsarbetare vid mekanisk verkstad",
      "Bleckvarufabriksarbetare",
      "Linnearbetare",
      "Skräddarearbetare",
      "Ciselör",
      "Textilarbetare Diversearbetare",
      "Mejerist",
      "Filare mekanisk verkstad",
      "Mekanisk verkstadslärling",
      "Verkstadsarbetare Plåtslagare",
      "Järnsvarvare vid stålpressningsverk",
      "Sågverksarbetare Smörjare",
      "Telefonväxelföreståndare",
      "Filare vid stålpressningsverk",
      "Fabriksarbetare Slipare",
      "Rullare å pappersbruk",
      "Maskinsnickare vid möbelfabrik",
      "Textilarbetare Tvinnerska",
      "Kullagerarbetare",
      "Knivsmed",
      "Fräsare Arbetare",
      "Järnarbetare Kockums",
      "Sömmerska Lägenhetsägare",
      "Linnesömmerska",
      "Filare Mekanisk verkstad",
      "Sågverksarbetare Eldare",
      "Textilarbetare Spinneri",
      "Smed Arbetare",
      "Stenarbetare vid stenindustri",
      "Kontorist textil",
      "Radiotelegrafist",
      "Järnvägsverkstadsförman",
      "Typograf Maskinsättare",
      "Mekaniker s. e.",
      "Gjutmästare",
      "Vågfabriksarbetare",
      "Rörläggningsarbetare",
      "Rörläggare Arbetare",
      "Kabelarbetare",
      "Knivarbetare",
      "Verkmästare vid pappersbruk",
      "Textilarbetare Smörjare",
      "Verkstadsarbetare Svarvare",
      "Järnarbetare vid mekanisk verkstad",
      "Sågverksarbetare Chaufför",
      "Textilarbetare Holm. br.",
      "Arbetare å Kalmar Bobin",
      "Svarvarbetare",
      "Virapassare Pappersbruk",
      "Klensmed vid järnbruk",
      "Hjälprullare Pappersbruk",
      "Mekanisk verkstadsarbetare",
      "Textilarbetare bom. väv.",
      "Valsarbetare",
      "Stärkelsefabriksarbetare",
      "Martinarbetare Järnverk",
      "Radiofabriksarbetare",
      "Toffelfabriksarbetare",
      "Maskinuppsättare",
      "Möbelsnickarearbetare",
      "Svarvare vid bobinfabrik",
      "Riktare",
      "Gelbgjutare",
      "Metalltryckare",
      "Fabriksarbetare Grovarbetare",
      "Linjeförman",
      "Sodabrännare vid pappersbruk",
      "Träullsfabriksarbetare",
      "Sågverksarbetare Kantare",
      "Verkmästare vid mekanisk verkstad",
      "Sågarbetare vid chokladfabrik",
      "Tråddragare järnbruk",
      "Slipare vid pappersbruk",
      "Cellulosafabriksarbetare Eldare",
      "Mekaniker s.e."
    ) ~ 1,
    TRUE ~ 0
  ))
```

```{r}
# create job type variable
df_reg_250 <- df_reg_250 %>%
  mutate(job_type = case_when(
    electricity_direct == 1 ~ "Direct electricity job",
    electricity_indirect == 1 ~ "Indirect electricity job",
    TRUE ~ "Other job"
  ))
```


```{r}
library(haven)
df_reg_250 %>% 
  mutate(schooling_abb = factor(schooling_abb)) %>% 
  select(-yrke.x) %>% 
  rename(yrke = yrke.y) %>% 
  write_dta("data/stata/Swedish-census-1930-clean-250km-threshold_job_types.dta", version = 15)
```


2. Descriptive statistics:

a. Calculate summary statistics for each job group, including mean income, median income, and income distribution within each parish type (electrified and non-electrified).

```{r}
df_reg_250 %>%
  filter(log_income_incl_zero > 0) %>%
  mutate(electricity_parish_living_in_lab = case_when(
    electricity_parish_living_in == 1 ~ "Treated",
    TRUE ~ "Control"
  )) %>%
  group_by(job_type, electricity_parish_living_in_lab) %>%
  summarise(
    mean_income = mean(log_income_incl_zero, na.rm = T),
    median_income = median(log_income_incl_zero, na.rm = T)
  )

```

```{r}
chunks <- seq(from = 0.01, to = 1, by = 0.075)

df_reg_250 %>%
  filter(log_income_incl_zero > 0) %>%
  mutate(electricity_parish_living_in_lab = case_when(
    electricity_parish_living_in == 1 ~ "Treated",
    TRUE ~ "Control"
  )) %>%
  filter(job_type != "Direct electricity job") %>% 
  group_by(job_type, electricity_parish_living_in_lab) %>%
  summarise(quantile = chunks,
            log_income_incl_zero = quantile(log_income_incl_zero, chunks)) %>% 
  ungroup() %>% 
  ggplot(aes(quantile, log_income_incl_zero, colour = electricity_parish_living_in_lab)) +
  geom_point() + 
  geom_line() +
  scale_x_continuous(labels = scales::percent_format()) +
  scale_y_continuous(limits = c(NA, 10)) +
  facet_wrap(~ job_type) +
  labs(
    y = "Log income",
    x = "Percentile of income distribution",
    title = "Income S-curves for 
                          <b><span style = 'color:#9C6114;'>treated</span></b> and 
                          <b><span style = 'color:#000080;'>control</span></b> individuals"
  ) +
  scale_colour_manual(values = c("#000080", "#9C6114")) +
  theme(
    # panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.title = element_markdown(size = 32, family = 'roboto'),
    plot.title.position = "plot",
    legend.position = "none",
    text = element_text(family = 'ibm', size = 18)
  ) 
  
ggsave(filename = here::here("summary_figs/income_job_type_plot.jpeg"), device = "jpeg", width = 290, height = 231, units = "mm", dpi = 300)
  
```


```{r}
df_reg_250 %>% 
  filter(between(age, 15, 45)) %>% 
  count(occ_hisco, sort = T)

df_reg_250 %>%
  filter(between(age, 15, 45)) %>%
  mutate(unemployed = is.na(occ_hisco) | occ_hisco == 99999) %>%
  group_by(tce_group_250) %>%
  summarize(pct_employed = mean(!unemployed)) %>%
  ungroup() %>%
  mutate(pct_unemployed = 1 - pct_employed) %>%
  mutate(
    tce_group_250 = str_to_title(tce_group_250),
    tce_group_250 = case_when(
      tce_group_250 == "Treatment" ~ "Treated",
      TRUE ~ tce_group_250
    )
  ) %>%
  pivot_longer(-tce_group_250) %>%
  mutate(name = case_when(
    name == "pct_employed" ~ "Employed",
    TRUE ~ "Unemployed"
  )) %>%
  mutate(value_label = scales::percent(value)) %>%
  ggplot(aes(value, tce_group_250, fill = name)) +
  geom_col() +
  scale_fill_manual(values = c("#6666ff", "#f0c389")) +
  geom_text(aes(label = value_label), hjust = 1.1, cex = 10) +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(
    x = "Share of labour force",
    y = NULL,
    title = "Share of labour force who are             <b><span style = 'color:#f0c389;'>unemployed</span></b> and 
                          <b><span style = 'color:#6666ff;'>employed</span></b>",
    fill = NULL
  ) +
  theme(
    # panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.title = element_markdown(size = 32, family = 'roboto'),
    plot.title.position = "plot",
    legend.position = "none",
    text = element_text(family = 'ibm', size = 32)
  ) 

ggsave(filename = here::here("summary_figs/employment_share.jpeg"), device = "jpeg", width = 290, height = 231, units = "mm", dpi = 300)
```


```{r}
# Your existing code to calculate the proportions
proportions_df <- df_reg_250 %>% 
  filter(between(age, 15, 45)) %>% 
  mutate(unemployed = is.na(occ_hisco) | occ_hisco == 99999) %>% 
  group_by(tce_group_250) %>% 
  summarize(pct_employed = mean(!unemployed)) %>% 
  ungroup()

# Get the proportions for each group
group1_employed <- proportions_df$pct_employed[proportions_df$tce_group_250 == 'control']
group2_employed <- proportions_df$pct_employed[proportions_df$tce_group_250 == 'treatment']

# Perform the t-test
ttest_result <- t.test(group1_employed, group2_employed)

# Print the results
print(ttest_result)
```


```{r}
df_reg_250 %>%
  filter(between(age, 15, 45)) %>%
  mutate(unemployed = is.na(occ_hisco) | occ_hisco == 99999) %>%
  group_by(tce_group_250, scbkod) %>%
  summarize(pct_employed = mean(!unemployed)) %>%
  ungroup() %>%
  mutate(pct_unemployed = 1 - pct_employed) %>%
  mutate(
    tce_group_250 = str_to_title(tce_group_250),
    tce_group_250 = case_when(
      tce_group_250 == "Treatment" ~ "Treated",
      TRUE ~ tce_group_250
    )
  ) %>% 
  ggplot(aes(pct_unemployed, fill = tce_group_250)) +
  geom_density(alpha = .5, adjust = .8) +
  scale_fill_manual(values = c("#6666ff", "#f0c389")) +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(
    x = "Share of labour force unemployed",
    y = NULL,
    title = "Share of unemployed in             <b><span style = 'color:#f0c389;'>treated</span></b> and 
                          <b><span style = 'color:#6666ff;'>control</span></b> parishes",
    fill = NULL
  ) +
  theme(
    # panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.title = element_markdown(size = 32, family = 'roboto'),
    plot.title.position = "plot",
    legend.position = "none",
    text = element_text(family = 'ibm', size = 32)
  ) 

ggsave(filename = here::here("summary_figs/employment_share_density.jpeg"), device = "jpeg", width = 290, height = 231, units = "mm", dpi = 300)
```



Okay so I am going to break my groups up - such that there is only the indirect and other jobs. 

b. Visualize the income distributions using histograms, box plots, or other suitable visualizations.

```{r}

df_reg_250 %>%
  ggplot(aes(log_income_incl_zero, fill = job_type)) +
  geom_density(adjust = 2) +
  facet_wrap(~ factor(electricity_parish_living_in), nrow = 2)

df_reg_250 %>%
  ggplot(aes(log_income_incl_zero, fill = factor(electricity_parish_living_in))) +
  geom_density(adjust = 2, alpha = 0.7) +
  facet_wrap(~ job_type, nrow = 2)


```


c. Calculate the number and proportion of workers in each job group who migrated to electrified parishes. 

What share of each group migrated to electricity parishes from not electricity parishes?

```{r}
df_reg_250 %>%
  group_by(job_type) %>%
  count(electricity_parish_living_in, electricity_parish_born) %>% 
  ungroup() %>% 
  mutate(migrated_in_to_electricity = case_when())
```



3. Difference-in-differences analysis:

a. To assess the income differences between the three job groups in electrified and non-electrified parishes, use a difference-in-differences (DID) approach. This will help you estimate the causal effect of electrification on income for each job group.

b. Set up a regression model with income as the dependent variable and electrification status, job group, and their interaction as independent variables. Include other relevant control variables as needed.

c. Estimate the model and interpret the coefficients on the interaction terms. These coefficients will represent the differences in income between electrified and non-electrified parishes for each job group. 

4. Migration analysis:

a. Create a categorical variable for the origin of migrants (e.g., urban, rural, or other parishes).

b. Calculate the proportions of workers in each job group who migrated to electrified parishes from different areas.

```{r}
df_reg_250 %>%
   group_by(job_type) %>%
   count(electricity_parish_living_in, electricity_parish_born) %>%
  ungroup() %>% 
  mutate(in_migrant = case_when(
    electricity_parish_living_in == 1 & electricity_parish_born == 0 ~ TRUE,
    TRUE ~ FALSE
  )) %>% 
  filter(electricity_parish_living_in == TRUE) %>% 
  group_by(job_type) %>% 
  mutate(share_in_migrant = n / sum (n))
```


```{r}
df_reg_250 %>% 
  count(scbkod == fscbkod) %>% 
  mutate(pct_share = n / sum(n))
  
  
df_reg_250 %>% 
  count(job_type)


df_reg_250 %>% 
  filter(!is.na(job_type), !is.na(electricity_parish_living_in)) %>% 
  lm(electricity_direct ~ electricity_parish_living_in, data = .) %>% 
  tidy()
```


Direct electricity jobs figure

```{r}

```


```{r}
library(margins)

# Probit regression
probit_model <- glm(electricity_direct ~ electricity_parish_living_in + age + , family = binomial(link = "probit"), data = df_reg_250 %>%
  filter(!is.na(job_type), !is.na(electricity_parish_living_in)))

# Calculate marginal effects
marginal_effects <- margins(probit_model, atmean = TRUE)

summary(marginal_effects)

```


```{r}
# Run probit regression with control variables
probit_model_controls <- glm(electricity_direct ~ electricity_parish_living_in + age + factor(hisclass_group_abb) + factor(schooling_abb) + factor(female), family = binomial(link = "probit"), data = df_reg_250 %>%
  filter(!is.na(job_type), !is.na(electricity_parish_living_in), !is.na(schooling_abb), !is.na(hisclass_group_abb)))

# Calculate average marginal effects
marginal_effects_controls <- margins(probit_model_controls, atmean = TRUE)

summary(marginal_effects_controls)

```





c. Perform a chi-square test or another appropriate statistical test to determine whether the distribution of migrants' origins differs significantly across the three job groups. 

5. Robustness checks and sensitivity analysis:

a. Test the robustness of your results by using alternative model specifications, such as fixed effects or random effects models.

b. Conduct sensitivity analyses by excluding potential outliers or by changing the criteria for job group classification. 

6. Interpretation and conclusion:

a. Summarize the main findings, addressing the research questions.

b. Discuss potential limitations of the study and offer suggestions for future research.



### Figures and tables

I want to make a figure that shows the direct electricity jobs - what are they - how much do they pay within their HISCO bracket?

```{r}
df_reg_250 %>% 
  filter(electricity_direct == 1) %>% 
  count(yrke.y, sort = T)
```


```{r}
df_reg_250 %>%
  group_by(hisclass_group_abb) %>%
  filter(electricity_direct == 1) %>%
  count(yrke.y, sort = T) %>%
  slice_max(hisclass_group_abb, n = 5, with_ties = FALSE) %>%
  select(-n) %>%
  ungroup()
```

To create this figure I will -

1. Get a sample of electricity related jobs

```{r}
library(tidytext)

df_reg_250 %>% 
  filter(!is.na(yrke.y),
         !yrke.y == "") %>% 
  group_by(job_type) %>% 
  count(yrke.y, sort = T) %>% 
  slice_max(n, n = 6) %>% 
  ungroup() %>% 
  mutate(yrke.y = str_to_title(yrke.y),
         yrke.y = reorder_within(yrke.y, n, job_type)) %>% 
  ggplot(aes(n, yrke.y, fill = job_type)) +
  geom_col() +
  scale_fill_brewer(palette = "Dark2") +
  facet_wrap(vars(job_type), scales = "free", nrow = 3) +
  scale_y_reordered() +
  labs(
    x = NULL,
    y = NULL,
    title = "Most common titles for our three job types",
    fill = NULL
  ) +
  theme(
    # panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.title = element_markdown(size = 32, family = 'roboto'),
    plot.title.position = "plot",
    legend.position = "none",
    text = element_text(family = 'ibm', size = 18)
  ) 

ggsave(filename = here::here("summary_figs/common_job_types.jpeg"), device = "jpeg", width = 290, height = 231, units = "mm", dpi = 300)
```


Education levels of electricity related workers?


```{r}
df_reg_250 %>% 
  filter(electricity_direct == 1) %>% 
  select(scbkod, fscbkod, yrke.y) %>% 
  write_rds(here::here("data", "temp", "direct_electricity_job_locations.rds"))

df_reg_250 %>% 
  filter(electricity_indirect == 1) %>% 
  select(scbkod, fscbkod, yrke.y) %>% 
  write_rds(here::here("data", "temp", "indirect_electricity_job_locations.rds"))
```

