---
title: "Export data to Stata May 2023"
format: html
---

# Read in data

```{r}
library(tidyverse)
df_reg <- read_rds(here::here("data", "clean_data", "df_ref.rds"))
```

/*******************************
* Research Outline
*******************************/

/**************************************
* 1. Completely Focused on the Shock 
**************************************/

## Treated parishes

TODO: Anything touching the Western Line in 1926 that is between the two hydro power stations.

```{r}

```


## Parishes and Controls:
// Are they balanced? 

```{r}
df_reg


```


// Structured Do Files:
// Create the shock in one file.
// Vary the shock. 

// Boundaries for the Control:
// Which boundaries should be used? 

// Age Span Shocked:
// Where do we make the age cutoffs?

// Save the Regression Data. 

// Structure Set:
// Balance tests based on different treatment and control groups.
// Decide on the main specification.
// Move the remainder to the appendix.

// Replication data does not have to be from the original 1930 census.
// Replication data must be anonymized and all unnecessary variables removed.

// Nice to Have:

/**************************************
* 2. Results 
**************************************/

// Unemployment:
// Number of people included in the census with no occupation listed or listed as unemployed.
// Compare treated to control groups.
// Do the jobs disappear comparing treated parishes to control parishes? 

// Income Effect without Controls:
// On average, how much more did they earn? 

// Income Effect with Controls:
// How much is due to what we can control for? 

// Inequality Results:
// Higher income shares up to the 80th percentile of the income distribution. 

// Wealth Aggregates and Wealth Inequality:
// (Optional)

/**************************************
* 3. Mechanisms 
**************************************/

// Structural Change as a Control and Mechanism:
// Probit for the probability of having an electricity-related job, conditional on being born in an electricity parish.
// Add the same regression, but with if you live in your parish of birth.
// Report the average stayer share being higher among treated parishes.
// Scale these coefficients for easy interpretation.
// "E.g., being born in an electricity parish raised your probability of having an electricity job by a factor of X."

/**************************************
* 4. Winners and Losers
**************************************/

// Income for Stayers and Movers - The Interaction. 

// Stayers without Electricity Jobs:
// Still had higher incomes.
// S-shaped graph. 

// Shocked by Electricity and Working in Agriculture:
// Do they have lower income compared to those not born in an electricity parish?
// Limited to farm workers.

// Are they more likely to live in another parish than their parish of birth?


```{r}

```
